### 2018-01-31 includes/experiment.tex
More typos and trailing whitespace.
First pass with Federico.
More edits from meeting.

\section{Experimental Data}
\label{sec:data}

@@

    \begin{figure}[h]
        \vspace{-0.2in}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}                   
            \vspace{-0.25in}
            \caption{Performance on concats-extracts-small} 
            \label{fig:concats-extracts-small}
        \end{subfigure}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}            
            \vspace{-0.25in}
            \caption{Performance on different-prefix}
            \label{fig:different-prefix}
        \end{subfigure}
        \vspace{-0.1in}
        \caption{Problems hard for \cvc{}}
        \label{fig:cvc-hard}
        \vspace{-0.3in}
    \end{figure}

    \begin{figure}[h]
    \vspace{-0.25in}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[width=\textwidth]{data/graphs/concats-balanced.png}
            \label{fig:concats-balanced}
            \vspace{-0.25in}
            \caption{Performance on concats-balanced}
        \end{subfigure}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[width=\textwidth]{data/graphs/concats-small.png}
            \label{fig:concats-small}
            \vspace{-0.25in}
            \caption{Performance on concats-small}
        \end{subfigure}
        \vspace{-0.1in}
        \caption{Problems hard for \us{}}
        \label{fig:z3str3-hard}
        \vspace{-0.3in}
    \end{figure}

\section{Usefulness to \us{}: A Case Study}
\label{sec:analysis}

We found a number of performance-related issues and opportunities for
new heuristics in \us{} thanks to \fuzzer{}. For example, the
instances in the \texttt{concats-big} suite generated by \fuzzer{}
helped us discover a missing heuristic. In particular, \us{} didn't
make full use of the solving context (e.g. some terms are empty
strings) to simplify the concatenations of a long list of string terms
before trying to reason about the equivalences among subterms. \us{}
therefore introduced a large number of unnecessary intermediate
variables and propagations.  As an immediate consequence of the
testing \us{} on \texttt{concats-big} benchmarks, we were able to
identify the factors common to these instances and rapidly formulate a
hypothesis as to why they were performing poorly. This allowed us to
move forward with the development of new heuristic to resolve this
issue and achieve better performance.

>>>>

\section{Experimental Data and Analysis}
\label{sec:data}

@@

\begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}
        \caption{Performance on concats-extracts-small}
        \label{fig:concats-extracts-small}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}
        \caption{Performance on different-prefix}
        \label{fig:different-prefix}
    \end{subfigure}
    \caption{Problems hard for \cvc{}}
    \label{fig:cvc-hard}

    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-balanced.png}
        \label{fig:concats-balanced}
        \caption{Performance on concats-balanced}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-small.png}
        \label{fig:concats-small}
        \caption{Performance on concats-small}
    \end{subfigure}
    \caption{Problems hard for \us{}}
    \label{fig:z3str3-hard}
\end{figure}

\subsubsection{Usefulness to \us{}: A Case Study}

We found a number of performance-related issues and opportunities for
new heuristics in \us{} thanks to \fuzzer{}. For example, the
instances in the \texttt{concats-big} suite generated by \fuzzer{}
helped us discover a missing heuristic. In particular, \us{} didn't
make full use of the solving context (e.g. some terms are empty
strings) to simplify the concatenations of a long list of string terms
before trying to reason about the equivalences among subterms. \us{}
therefore introduced a large number of unnecessary intermediate
variables and propagations. As an immediate consequence of
testing \us{} on \texttt{concats-big} benchmarks, we were able to
identify the factors common to these instances and rapidly formulate a
hypothesis as to why they were performing poorly. This allowed us to
move forward with the development of a new heuristic to resolve this
issue and achieve better performance.

### 2018-01-31 includes/introduction.tex
More edits from meeting.

\begin{enumerate}
\item \textbf{The \fuzzer{} tool}:
    In section~\ref{sec:fuzzer}, we describe a modular fuzzer that can
    transform and randomly generate \smtfull{} string and regular
    expression (regex) problems.\footnote{We assume basic
    familiarity with string solvers and their input
    language.} Scaling inputs (e.g., long string
    constants, deep concatenations) are particularly useful in
    identifying asymptotic behaviors in solvers, and \fuzzer{}.
    We briefly document \fuzzer{}'s
    components and modular architecture. We provide example use cases to
    demonstrate its utility as an exploratory tool for validating
    solvers.

@@

\item \textbf{Experimental Results and Analysis}:
    We compare the performance of \theSolvers{} on the
    the \fuzzer{} suites \theSuites{} in section~\ref{sec:data}. We highlight
    these suites because they make some solvers perform poorly,
    but not others. In section~\ref{sec:analysis}, we analyze our
    experimental results, and pinpoint algorithmic limitations
    in \us{} that cause poor performance. We propose enhancements that
    address these issues, which \fuzzer{} helped us find.
\end{enumerate}

>>>>

\begin{enumerate}
\item \textbf{The \fuzzer{} tool}:
    In section~\ref{sec:fuzzer}, we describe a modular fuzzer that can
    transform and randomly generate \smtfull{} string and regular
    expression (regex) problems.\footnote{We assume basic
    familiarity with string solvers and their input
    language.} SScaling inputs (e.g., long string constants,
    deep concatenations) are particularly useful in identifying asymptotic
    behaviors in solvers, and \fuzzer{} has many options to generate such
    scaling inputs. We briefly document \fuzzer{}'s
    components and modular architecture. We provide example use cases to
    demonstrate its utility as an exploratory tool for validating
    solvers.

    % Further, StringFuzz's modular design lets users extend it to generate scaling inputs along any parameter of the   input constraint.

@@

\item \textbf{Experimental Results and Analysis}:
    We compare the performance of \theSolvers{} on the
    the \fuzzer{} suites \theSuites{} in section~\ref{sec:data}. We highlight
    these suites because they make some solvers perform poorly,
    but not others. We analyze our
    experimental results, and pinpoint algorithmic limitations
    in \us{} that cause poor performance. We propose enhancements that
    address these issues, which \fuzzer{} helped us find.
\end{enumerate}
